Wissenschaftliches Arbeiten

### 2014-06-29 paper.tex
Rewriting parts of the restaurant examples explaining the preference aggregation and the combinatorial domains

The prerequisite for the following sub fields of social choice theory is the one of preference aggregation. It tries to formalize the given choices together with the agents' preferences and aggregate them together to a single preference. The formalization also differs from study object to study object. For instance when eating out with colleagues and trying to compromise on a restaurant you can choose in two ways: Either each quantifies each location with a number for his or her preference. This would be a cardinal preference. In contrast a qualitative approach is used when each compiles an order which then would be ordinal preferences.~\cite[Chapter~2]{BCE12}

@@

So far we have presented some different areas of social choice theory but in order to understand the topic of this paper - Combinatorial Auctions - we also have to explain the background of combinatorial domains in general.

Once again -- to demonstrate the core of combinatorial domains -- a restaurant example: This time the topic is the ordering and the colleagues have to choose from a starter, a main dish and a wine. They all will only get what they have voted for. Imagine that they follow the given order and are in the process to vote about the starter. One of them has no preference of the wine type but only wants to eat fish as main course if white wine is chosen. Also he or she has a preference for fish as main course and does not have a clue what type of wine the others will choose.\footnote{They are not allowed to communicate for the example's sake.} In that situation he or she can choose to risk the fish main course and be disappointed if red wine is chosen or be on the safe side and be a bit mad when white wine is chosen after all.

>>>>

The prerequisite for the following sub fields of social choice theory is the one of preference aggregation. It tries to formalize the given choices together with the agents' preferences and aggregate them together to a single preference. The formalization also differs from study object to study object. For instance when eating out with colleagues and trying to compromise on a restaurant you can choose in two ways: Either each quantifies each location with a number for his or her preference. This would be a cardinal preference. In contrast a qualitative approach is used when each compiles an ordered list of restaurants which then would be ordinal preferences.~\cite[Chapter~2]{BCE12}

@@

So far we have presented some different areas of social choice theory but in order to understand the topic of this paper -- Combinatorial Auctions -- we also have to explain the background of combinatorial domains in general.

Once again -- to demonstrate the need for combinatorial domains -- a restaurant example: This time the topic is ordering and the colleagues have to choose a main dish and wine. They all will get the same dish/wine which has the most votes. Imagine that they follow the given order, first main course, then wine, and are currently voting for the main course.

One of the co-workers has no distinct preference of any wine type but only wants to eat fish if white wine is chosen. Also he or she has a preference for fish over the other available main dishes and does not have a clue what type of wine the others will choose.\footnote{They are not allowed to communicate for the example's sake.} In that situation he or she can choose to risk the fish and be disappointed if red wine is chosen afterwards, or be on the safe side by choosing a different main course and be a bit mad if white wine is chosen after all.

### 2014-06-29 review-log.tex
Replacing tupel brackets with a better version of them
Fixing an argument
Rewriting parts of the restaurant examples explaining the preference aggregation and the combinatorial domains

\section{Language \& Style}
\subsection{However sometimes either the wording is confusing or I do not get the message right. E.g. ``Another fairness criteria could be that the minimum utility is maximized.'' (1)}
Rephrased and extended.
\subsection{Another point is that it is more common to use cannot instead of `can not' and another instead of `an other'. (1)}
Searched and Replaced.
\subsection{Im Großen und Ganzen in Ordnung. Ein Zeitfehler in Kapitel 3, letzter Absatz: ``From this set they chose that'', hier gehört choose(Gegenwart) (2)}
Corrected typo.
\subsection{In section 4 Bidding Representations \& Languages the article says ``To be equivalent to the naive form these atomic bid must also be OR-conjunctional so that a bidder can submit several bundle he or she wants to bid for.'' The word bundle is missing the -s ending for plural. (3)}
Corrected typo.
\subsection{Use of correct/better brackets in section 3 instead of less-than and greater-than signs. (3)}
\subsection{On page six the paper says ``During the previous section some small examples were already given but the following ones will go a bit deeper into real work applications.'' I think there is a typo and it should say real world applications. (3)}
Corrected auto correction.

\section{Topic Mistakes}
\subsection{On page fife the article says ``[BCE12, pp. 46–47] shows that this `Winner Determination Problem' can be converted into the `Set Packing Problem' which is known to be NP-hard.'' But [BCE12] reduces ``Set Packing Problem'' to ``Winner Determination Problem'' in order to show NP-hardness of the ``Winner Determination Problem''. That is, the other way around. Furthermore he states that it is NP-complete. (3)}

\section{Clarity}
\subsection{In Kapitel 1.2, letzter Satz geht nicht ganz klar hervor was ``ordinal preference'' bedeutet. (2)}
\subsection{In the restaurant example in section 1.5 Combinatorial Domains it is not clear at first glance that the author does not use a combinatorial voting system. (3)}
\subsection{In section 4 Bidding Representations \& Languages I think the part about XOR-bids can benefit from some more explanations. I feel that it would be easier to understand, if the the dummy items would have been explained further. [FLBS99] actually has a better example.}
\subsection{On page five the article says ``Its upper limit is $O(n^n)$.'' without saying what n is. (3)}

>>>>

\section{Language \& Style}
\subsection{However sometimes either the wording is confusing or I do not get the message right. E.g. ``Another fairness criteria could be that the minimum utility is maximized.'' (1)}
Rephrased and extended.
\subsection{Another point is that it is more common to use cannot instead of `can not' and another instead of `an other'. (1)}
Searched and Replaced.
\subsection{Im Großen und Ganzen in Ordnung. Ein Zeitfehler in Kapitel 3, letzter Absatz: ``From this set they chose that'', hier gehört choose(Gegenwart) (2)}
Corrected typo.
\subsection{In section 4 Bidding Representations \& Languages the article says ``To be equivalent to the naive form these atomic bid must also be OR-conjunctional so that a bidder can submit several bundle he or she wants to bid for.'' The word bundle is missing the -s ending for plural. (3)}
Corrected typo.
\subsection{Use of correct/better brackets in section 3 instead of less-than and greater-than signs. (3)}
Replaced all tupel brackets with \langle and \rangle. Also fixed two missing set brackets.
\subsection{On page six the paper says ``During the previous section some small examples were already given but the following ones will go a bit deeper into real work applications.'' I think there is a typo and it should say real world applications. (3)}
Corrected auto correction.

\section{Topic Mistakes}
\subsection{On page five the article says ``[BCE12, pp. 46–47] shows that this `Winner Determination Problem' can be converted into the `Set Packing Problem' which is known to be NP-hard.'' But [BCE12] reduces ``Set Packing Problem'' to ``Winner Determination Problem'' in order to show NP-hardness of the ``Winner Determination Problem''. That is, the other way around. Furthermore he states that it is NP-complete. (3)}
Corrected.

\section{Clarity}
\subsection{In Kapitel 1.2, letzter Satz geht nicht ganz klar hervor was ``ordinal preference'' bedeutet. (2)}
Extended the example a bit.
\subsection{In the restaurant example in section 1.5 Combinatorial Domains it is not clear at first glance that the author does not use a combinatorial voting system. (3)}
Redefined the example a bit by stripping not needed parts and reworked the text in general.
\subsection{In section 4 Bidding Representations \& Languages I think the part about XOR-bids can benefit from some more explanations. I feel that it would be easier to understand, if the the dummy items would have been explained further. [FLBS99] actually has a better example.}
\subsection{On page five the article says ``Its upper limit is $O(n^n)$.'' without saying what n is. (3)}
